Supplement to: Library Learning in Neurally-Guided Bayesian Program Induction

### 2018-10-26 supplement.tex
almost, ready

>>>>

\section{An Illustration of the three steps of our algorithm}
Below we diagram the steps employed by our algorithm. At each step of the algorithm,
we have shaded the observed variables in gray and left the unobserved variables white.
Black lines correspond to a connection from the top-down
generative model, while red lines correspond to connections from the bottom-up recognition model.
\begin{figure}[h]
\centering
%  \includegraphics{figures/iterations.eps}
\begin{tikzpicture}
  \begin{scope}[shift={(2.5,0)}]
    \node[obs] at (3,3) (dx){$\mathcal{D}$};
    \node[latent] at (3.5,1.75) (zp){$p$};
    \node[obs] at (4,3) (tx){$\theta^{(x)}$};
    \node[obs] at (3.5,0.7) (xp) {$x$};
    \node[align = center] at ([yshift = -0.6cm,xshift = 0.5cm]xp.south) {Explore: Infer $p$};
    \draw [->,red] (xp.east) to[out = 0,in = 0] node(nn){} (tx.east);
    \draw [->,red] (tx) -- (zp);
    \draw [->] (dx) -- (zp);
    \node at (nn) {
      \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.2,shift={+(-1,2.5)}}]
        \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
        \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
        \node[rectangle] at (1,1) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (I-\name) at (0,-\y) {};
        \foreach \name / \y in {1,...,3}
            \node[neuron] (H-\name) at (1,-\y-0.5) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (O-\name) at (2,-\y) {};
        \foreach \source in {1,...,4}
            \foreach \dest in {1,...,3}
                \draw [-latex] (I-\source) -- (H-\dest);
        \foreach \source in {1,...,3}
            \foreach \dest in {1,...,4}
                \draw [-latex] (H-\source) -- (O-\dest);
      \end{tikzpicture}
    };
    \node[shift={+(0,-0.65)}] at (nn) [fill=white]{ $q(x)$ };
  \end{scope}
  \begin{scope}[shift={(0.7,-4.2)}]
    \node[obs] at (3,3) (dt){$\mathcal{D},\theta$};
    \node[obs] at ([yshift = -0.7cm,xshift = 0.0cm]dt.south) (p2){$p_2$};
    \node[obs] at ([yshift = -0.7cm,xshift = 0.0cm]p2.south) (x2){$x_2$};
    \draw [->] (p2.south) -- (x2.north);
    \draw [->] (dt.south) -- (p2.north);
    \node[obs] at ([yshift = 0cm,xshift = -0.5cm]p2.west) (p1){$p_1$};
    \node[obs] at ([yshift = -0.7cm,xshift = 0.0cm]p1.south) (x1){$x_1$};
    \draw [->] (p1.south) -- (x1.north);
    \draw [->] (dt.south) -- (p1.north);
    \node[obs] at ([yshift = 0cm,xshift = 0.5cm]p2.east) (p3){$p_3$};
    \node[obs] at ([yshift = -0.7cm,xshift = 0.0cm]p3.south) (x3){$x_3$};
    \draw [->] (p3.south) -- (x3.north);
    \draw [->] (dt.south) -- (p3.north);
    \node at ([yshift = 0cm,xshift = 0.3cm]p3.east) {$\cdots $};
    \node at ([yshift = 0cm,xshift = 0.3cm]x3.east) {$\cdots $};

    \node[obs] at ([yshift = 0cm,xshift = 1.3cm]p3.east) (zp){$p$};
    \node[obs] at ([yshift = 0cm,xshift = 1.3cm]x3.east) (xp) {$x$};
    \draw [->] (zp.south) -- (xp.north);
    \plate {}{(zp)(xp)}{$x\in X$};
    \draw[dashed,cyan,very thick] ([yshift = 0.5cm,xshift = -2]p1.west)
    rectangle  ([yshift = -0.45cm,xshift = +2]xp.east);
    \node[align = center] at ([yshift = -1cm,xshift = 0.6cm]x2.south) {Compile: Train $q$\\training data: cyan $(x,p)$};
  \end{scope}

  \begin{scope}[shift={(7.7,-4)}]
    \node[latent] at (0.5,3) (d){$\mathcal{D}$};
    \node[latent] at (1.5,3) (t){$\theta$};
    \node[obs] at (1,1.75) (z){$p$};
%     \node[latent] at (3.5,1.5) (tx){$\theta^{(x)}$};
    \node[obs] at (1,0.5) (x) {$x$};
    \edge {z}{x};
    \edge {d,t}{z};
    \plate {}{(z)(x)}{$x\in X$};
    \node[align = center] at ([yshift = -1cm]x.south) {Compress: Induce $(\mathcal{D},\theta)$};
  \end{scope}
\end{tikzpicture}
\end{figure}
